\anonsection{Список использованной литературы}
{\def\section*#1{}
\begin{thebibliography}{99}
\bibitem{Agranovskiy} Аграновский А. В., Балакин А. В., Грибунин В. Г., Сапожников С. А. Стеганография, цифровые водяные знаки и стеганоанализ. Монография. — М.: Вузовская книга, 2009. 220 с.
\bibitem{HideAndSeek} N.F. Johnson, S. Jajodia, Steganalysis of images created using current steganography software, in: Lecture Notes in Computer Science, vol. 1525,
Springer-Verlag, Berlin, 1998, pp. 273–289.
\bibitem{GNCNN} Qian, Y. Deep learning for steganalysis via convolutional neural networks / Y. Qian, J. Dong, W. Wang, T. Tan // Proc. SPIE 9409: сб. тр. участников конф. Media Watermarking, Security, and Forensics 2015. – 2015.
\bibitem{FridrichNoiseResidual} Fridrich, J. Steganalysis of content-adaptive steganography in spatial domain / J. Fridrich, J. Kodovsky, V. Holub, M. Goljan // LNCS 6958: сб. тр. участников конф. 13th Information Hiding Workshop. – 2011. – С. 102-117.
\bibitem{FrenchCNN} Steganalysis via a Convolutional Neural Network using Large Convolution Filters for Embedding Process with Same Stego Key [Электронный ресурс] : статья из сетевого хранилища научных материалов / J.-F. Couchot, R. Couturier, C. Guyeux, M. Salomon. – Режим доступа: https://arxiv.org/abs/1605.07946
\bibitem{SirotaHIC} Сирота, А. А. Метод создания цифровых водяных знаков на основе гетероассоциативных сжимающих преобразований изображений и его реализация с использованием искусственных нейронных сетей / А. А. Сирота, М. А. Дрюченко, Е. Ю. Митрофанова // Компьютерная оптика. – 2018. – № 3. – С. 483-494. 
\bibitem{ZhaoKoch} Zhao, J. Embedding Robust Labels into Images for Copyright Protection / J. Zhao, E. Koch // Proceeding of the Int. Congress on Intellectual Property Rights for Specialized Information, Knowledge and New Techniques. – 1995. – С. 242-251.
\bibitem{KochZhao} Koch, E. Towards Robust and Hidden Image Copyright Labeling / E. Koch, J. Zhao // IEEE Workshop on Nonlinear Signal and Image Processing. – 1995. – С. 123-132.
\bibitem{WOW} Holub, V. Designing steganographic distortion using directional filters / V. Holub, J. Fridrich // The IEEE International Workshop on Information Forensics and Security. – 2012. – С. 234-239.
\bibitem{PPG-LIRMM-COLOR} PPG-LIRMM-COLOR base [Электронный ресурс]. – Режим доступа: http://www.lirmm.fr/~chaumont/PPG-LIRMM-COLOR.html
\bibitem{ppmtopgm} Ppmtopgm User Manual [Электронный ресурс]. – Режим доступа: http://netpbm.sourceforge.net/doc/ppmtopgm.html
\end{thebibliography}
}
\clearpage
